Pillar 1 - Sequential Pattern Mining

### 2019-01-25 Pillar 1 - Sequential Pattern Mining.Rmd
minor change

AR <- apriori(
  data = transactions, 
  parameter = list(
    supp = 0, # min support
    smax = 1,    # max support
    conf = 0,    # min confidence
    minlen = 2,  # min length of rule
    maxlen = 2,  # max length of rule
    ext = TRUE,
    arem = "diff",
    aval = TRUE,
    minval = 0
    ),
  appearance = list(
    #lhs = c("HUM1003"),
    #rhs = c("HUM1007", "HUM1010")
  ),
  control = list(
    verbose = FALSE
  )
  ) %>%
  inspect

>>>>

AR <- apriori(
  data = transactions, 
  parameter = list(
    supp = 0, # min support
    smax = 1,    # max support
    conf = 0,    # min confidence
    minlen = 2,  # min length of rule
    maxlen = 2,  # max length of rule
    ext = TRUE,
    arem = "diff",
    aval = TRUE,
    minval = 0
    ),
  appearance = NULL,
  control = list(
    verbose = FALSE
  )
  ) %>%
  inspect
